Exploring mathematical objects from custom-tailored mathematical universes

### 2020-06-21 paper-filmat.tex
Include more stills and video of family (in response to review)

\usepackage[utf8]{inputenc}
\usepackage{amsthm,mathtools,amssymb,graphicx,ragged2e,extpfeil}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing}
\usepackage{booktabs,framed}
\usepackage[all]{xy}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{xspace}

@@

\begin{figure}
  \includegraphics[height=3cm]{zeros-in-families-still}
  \caption{\label{fig:ivt} A single member~$f_{x_0}$ of a continuous
  family~$(f_x)_{x \in X}$ of continuous functions~$f_x : \RR \to \RR$. The
  parameter space is~$X = [0,1]$ (not shown) and the other functions~$f_x$ are
  obtained from~$f_{x_0}$ by moving the horizontal plateau further up or
  down. The depicted member~$f_{x_0}$ has a unique
  zero and there is an open neighborhood~$U$ of~$x_0$ on which zeros of the
  functions~$f_x$, $x \in U$ can be picked continuously. However, there is no
  such neighborhood of that particular parameter value~$x_1$ for which the
  horizontal plateau lies on the $x$-axis.}
\end{figure}

>>>>

\usepackage[utf8]{inputenc}
\usepackage{amsthm,mathtools,amssymb,graphicx,ragged2e,extpfeil}
\usepackage{tikz}
\usetikzlibrary{calc,shapes,shapes.callouts,shapes.arrows,patterns,fit,backgrounds,decorations.pathmorphing}
\usepackage{booktabs,framed}
\usepackage[all]{xy}
\usepackage[protrusion=true,expansion=true]{microtype}
\usepackage{xspace}
\usepackage{marginnote,animate,ocgx2}

@@

\begin{figure}
\marginnote{
  \begin{ocg}[printocg=never]{layername}{layerid1}{on}
    \vspace*{-12em}
    \scalebox{0.2}{
      \animategraphics[loop,autoplay]{60}{zeros-in-families-frames/}{0000}{0188}
    }
    \begin{minipage}{3cm}\scriptsize\noindent
    In the online version of this contribution, a video of the
    continuous family can be seen here.\end{minipage}
  \end{ocg}}
  \includegraphics[height=3cm]{zeros-in-families-still-1}
  \includegraphics[height=3cm]{zeros-in-families-still-2}
  \includegraphics[height=3cm]{zeros-in-families-still-3}

  \caption{\label{fig:ivt}Three members~$f_{x_0}, f_{x_1}, f_{x_2}$ of a continuous
  family~$(f_x)_{x \in X}$ of continuous functions~$f_x : \RR \to \RR$. The
  parameter space is~$X = [0,1]$ (not shown). The functions~$f_x$ are
  obtained by moving the horizontal plateau up or
  down. The leftmost depicted member~$f_{x_0}$ has a unique
  zero, and there is an open neighborhood~$U$ of~$x_0$ on which zeros of the
  functions~$f_x$, $x \in U$ can be picked continuously. The same is true
  for~$x_2$ (right figure). However, there is no
  such neighborhood of that particular parameter value~$x_1$ for which the
  horizontal plateau lies on the $x$-axis (middle figure).}
\end{figure}
